cardinalR: Generating interesting high-dimensional data structures

### 2025-10-12 paper-cardinalR.Rmd
Added draft image for the implementation

<!--https://cran.r-project.org/web/packages/surreal/index.html-->
<!--https://cran.r-project.org/web/packages/DHARMa/vignettes/DHARMa.html-->

@@

@@

<!-- ## Web site -->

<!-- More documentation of the package can be found at the web site [https://jayanilakshika.github.io/cardinalR/](https://jayanilakshika.github.io/cardinalR/). -->

>>>>

@@

```{r, out.width = "100%"}
knitr::include_graphics("figures/cardinalR.pdf")
```

@@
